Paper 2, Econ 980x

### 2022-12-09 Paper2.Rmd
commit

@@

@@

delta3 <- change %>%
  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
summary(delta3)

@@

```{r}

>>>>

```{r cashe data, cache = TRUE}

@@

# race
csv %>%
  count(race, sort = TRUE) %>%
  filter(n > 1000)

#We can see that top 5 groups > 1000 people

csv <- csv %>%
  filter(race %in% c("White only", "Black only", "Asian only", "American Indian, Alaskan Native", "White-American Indian"))

@@

delta3 <- change4 %>%
  lm(formula = leisure_change ~ gender+ new_educ+ nchild+ marst_simple)
summary(delta3)

@@

```{r time-year-gender effects}

summary(newcsv1)

time_model <- newcsv1 %>%
  lm(formula = bls_leis ~ gender*year + age + race*new_educ)

summary(time_model)
